
\documentclass[12pt,a4paper]{article}

% ── Packages ─────────────────────────────────────────────────────────────
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[margin=2.5cm]{geometry}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{tcolorbox}
\usepackage{booktabs}
\usepackage{array}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{fontawesome5}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{parskip}
\usepackage{longtable}

% ── Colour Palette ─────────────────────────────────────────────────────
\definecolor{adminRed}{HTML}{C0392B}
\definecolor{adminAccent}{HTML}{E74C3C}
\definecolor{adminGold}{HTML}{F39C12}
\definecolor{adminGreen}{HTML}{06A77D}
\definecolor{eyantraWarn}{HTML}{F4A261}
\definecolor{codebg}{HTML}{F4F6F9}
\definecolor{codeborder}{HTML}{CDD4E0}
\definecolor{lightgray}{HTML}{F8F9FA}
\definecolor{darkgray}{HTML}{495057}

% ── Hyperlinks ─────────────────────────────────────────────────────────
\hypersetup{
  colorlinks=true,
  linkcolor=adminAccent,
  urlcolor=adminAccent,
  pdftitle={EEP Auto-Grading Platform -- Admin Guide},
  pdfauthor={E-Yantra, IIT Bombay},
}

% ── Code Listing Style ─────────────────────────────────────────────────
\lstdefinestyle{shellstyle}{
  backgroundcolor=\color{codebg},
  basicstyle=\ttfamily\small,
  breaklines=true,
  frame=single,
  rulecolor=\color{codeborder},
  framesep=4pt,
  xleftmargin=6pt,
  xrightmargin=6pt,
  showstringspaces=false,
  keywordstyle=\color{adminRed}\bfseries,
  commentstyle=\color{darkgray}\itshape,
  stringstyle=\color{adminGreen},
}
\lstset{style=shellstyle}

% ── Custom tcolorbox environments ──────────────────────────────────────
\tcbuselibrary{skins,breakable}

\newtcolorbox{infobox}[1][Note]{
  colback=adminAccent!8,
  colframe=adminAccent,
  fonttitle=\bfseries,
  title={\faInfoCircle\enspace #1},
  breakable,
}

\newtcolorbox{warnbox}[1][Warning]{
  colback=eyantraWarn!12,
  colframe=eyantraWarn!80!black,
  fonttitle=\bfseries,
  title={\faExclamationTriangle\enspace #1},
  breakable,
}

\newtcolorbox{dangerbox}[1][Critical]{
  colback=adminRed!8,
  colframe=adminRed,
  fonttitle=\bfseries,
  title={\faSkull\enspace #1},
  breakable,
}

\newtcolorbox{tipbox}[1][Admin Tip]{
  colback=adminGreen!10,
  colframe=adminGreen,
  fonttitle=\bfseries,
  title={\faUserShield\enspace #1},
  breakable,
}

% ── Section Title Styling ──────────────────────────────────────────────
\titleformat{\section}
  {\Large\bfseries\color{adminRed}}
  {\thesection}{1em}{}[\color{adminAccent}\rule{\linewidth}{1.5pt}]

\titleformat{\subsection}
  {\large\bfseries\color{adminRed}}
  {\thesubsection}{0.8em}{}

\titleformat{\subsubsection}
  {\normalsize\bfseries\color{darkgray}}
  {\thesubsubsection}{0.7em}{}

% ── Header / Footer ───────────────────────────────────────────────────
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\color{adminRed}\small\bfseries EEP Auto-Grading Platform}
\fancyhead[R]{\color{darkgray}\small Administrator Guide}
\fancyfoot[C]{\color{darkgray}\small\thepage}
\renewcommand{\headrulewidth}{0.5pt}
\renewcommand{\headrule}{\color{adminAccent}\hrule width\headwidth height\headrulewidth}

% ── Step counter ──────────────────────────────────────────────────────
\newcounter{stepnum}
\newcommand{\step}[1]{%
  \stepcounter{stepnum}%
  \vspace{6pt}%
  \noindent\colorbox{adminRed}{\color{white}\bfseries\small\ Step \thestepnum\ }%
  \hspace{4pt}\textbf{#1}\\[4pt]%
}

% ─────────────────────────────────────────────────────────────────────
\begin{document}
% ─────────────────────────────────────────────────────────────────────

% ── Title Page ────────────────────────────────────────────────────────
\begin{titlepage}
  \centering
  \vspace*{2cm}

  {\color{adminRed}\rule{\linewidth}{3pt}}
  \vspace{0.5cm}

  {\Huge\bfseries\color{adminRed} EEP Auto-Grading Platform}\\[0.6em]
  {\LARGE\color{adminAccent} Administrator Guide}\\[0.4em]
  {\large\color{darkgray} E-Yantra Summer Internship Program (EYSIP)}

  \vspace{0.5cm}
  {\color{adminRed}\rule{\linewidth}{3pt}}

  \vspace{1.5cm}

  \begin{tcolorbox}[colback=lightgray, colframe=adminAccent, width=0.88\linewidth]
    \centering
    \large This guide covers \textbf{platform-wide administration}: \\
    user management, assignment oversight, system health,\\
    platform configuration, and security operations.
  \end{tcolorbox}

  \vfill

  \begin{tabular}{rl}
    \textbf{Document Version:} & 1.0 \\
    \textbf{Platform Version:} & v2.0 \\
    \textbf{Audience:}         & Platform Administrators (ADMIN role) \\
    \textbf{Organisation:}     & E-Yantra, IIT Bombay \\
  \end{tabular}

  \vspace{1cm}
  {\color{darkgray}\small Last updated: \today}
\end{titlepage}

% ── Table of Contents ─────────────────────────────────────────────────
\tableofcontents
\newpage

% ─────────────────────────────────────────────────────────────────────
\section{Overview}
% ─────────────────────────────────────────────────────────────────────

The \textbf{Admin} role has full platform-wide access. Admins can:

\begin{itemize}[leftmargin=*]
  \item View and manage \textbf{all students and mentors} on the platform
  \item Create new \textbf{mentor/admin accounts}
  \item Override \textbf{assignment restrictions} (publish any assignment, modify deadlines)
  \item View \textbf{all submissions} and grading sessions across the entire platform
  \item Access \textbf{system health} metrics (database, Redis, worker status)
  \item Manage \textbf{platform configuration} via environment variables
  \item Perform \textbf{security operations} (reset passwords, deactivate accounts)
\end{itemize}

\begin{dangerbox}[Admin Responsibility]
  The admin account has unrestricted access. Protect credentials carefully. The default admin password is the email address -- change it immediately after first deployment.
\end{dangerbox}

% ─────────────────────────────────────────────────────────────────────
\section{Admin Dashboard}
% ─────────────────────────────────────────────────────────────────────

Login with the admin account. The admin dashboard shows platform-wide stats:

\begin{center}
\begin{tabularx}{\linewidth}{>{\bfseries}lX}
\toprule
Widget & Scope \\
\midrule
Total Students    & All students registered on the platform \\
Total Mentors     & All mentor accounts \\
Total Submissions & All submissions across all assignments \\
Active Sessions   & Submissions currently being processed \\
System Health     & Database and Redis connectivity status \\
\bottomrule
\end{tabularx}
\end{center}

% ─────────────────────────────────────────────────────────────────────
\section{User Management}
% ─────────────────────────────────────────────────────────────────────

\subsection{Viewing All Students}

\begin{enumerate}
  \item Navigate to \textbf{Users $\rightarrow$ Students} in the sidebar.
  \item You can see all registered students with their roll number, email, active status, and registration date.
  \item Use the search field to filter by roll number or name.
\end{enumerate}

\subsection{Viewing All Mentors}

\begin{enumerate}
  \item Navigate to \textbf{Users $\rightarrow$ Mentors}.
  \item Displays all mentor accounts with their role (MENTOR or ADMIN).
\end{enumerate}

\subsection{Creating a Mentor Account}

\setcounter{stepnum}{0}

\step{Navigate to Users $\rightarrow$ Mentors}

\step{Click \textbf{+ Create Mentor}}
Fill in the following fields:

\begin{center}
\begin{tabularx}{\linewidth}{>{\bfseries}lX}
\toprule
Field & Description \\
\midrule
Username  & The mentor's login username (typically their email) \\
Full Name & Mentor's display name \\
Email     & Email address (must be unique) \\
Password  & Initial password. Communicate this securely to the mentor. \\
Role      & \texttt{mentor} for a regular mentor, \texttt{admin} for an administrator \\
\bottomrule
\end{tabularx}
\end{center}

\step{Click \textbf{Create}} -- The account is active immediately.

\begin{warnbox}
  Communicate the initial password to the mentor via a secure channel (not plain email). Ask them to change it on first login.
\end{warnbox}

\subsection{Deactivating Accounts}

To deactivate a student or mentor account (blocking login without deleting data):
\begin{enumerate}
  \item Locate the user in the Users list.
  \item Toggle the \textbf{Active} switch to off.
  \item The user will receive a 401 Unauthorized on their next login attempt.
\end{enumerate}

% ─────────────────────────────────────────────────────────────────────
\section{Assignment Management (Admin)}
% ─────────────────────────────────────────────────────────────────────

As an admin you have \emph{no ownership restrictions} on assignments.

\subsection{Viewing All Assignments}

Navigate to \textbf{Assignments $\rightarrow$ All Assignments} (admin view). This shows all assignments regardless of published/unpublished/archived status.

\subsection{Admin Update (Full Override)}

Use the admin assignment update endpoint to modify \emph{any} field on \emph{any} assignment:

\begin{lstlisting}
PATCH /api/v1/assignments/admin/{assignment_id}

Body (all fields optional):
{
  "title": "Updated Title",
  "description": "New description",
  "max_score": 100,
  "deadline": "2025-12-31T23:59:59",
  "is_published": true,
  "is_archived": false,
  "late_penalty_pct": 10,
  "resource_links": ["https://example.com/resource"]
}
\end{lstlisting}

\begin{tipbox}
  Unlike mentor updates, the admin update has \textbf{no deadline lock}. You can extend deadlines even after they have passed.
\end{tipbox}

\subsection{Archiving / Deleting Assignments}

Assignments are never hard-deleted. Use the admin archive endpoint:

\begin{lstlisting}
DELETE /api/v1/assignments/admin/{assignment_id}
\end{lstlisting}

This sets \texttt{is\_archived = true}, hiding the assignment from all views while preserving all submissions and results.

% ─────────────────────────────────────────────────────────────────────
\section{Submission \& Session Oversight}
% ─────────────────────────────────────────────────────────────────────

\subsection{All Submissions}

Navigate to \textbf{Results $\rightarrow$ All Submissions}. Admins see submissions across all mentors' assignments.

\begin{center}
\begin{tabularx}{\linewidth}{>{\bfseries}lX}
\toprule
API Endpoint & Purpose \\
\midrule
GET /api/v1/admin/submissions & All submissions, any assignment \\
GET /api/v1/admin/sessions    & All grading sessions \\
GET /api/v1/admin/students    & All students \\
GET /api/v1/admin/mentors     & All mentor accounts \\
\bottomrule
\end{tabularx}
\end{center}

\subsection{Grading Sessions}

A \emph{grading session} corresponds to a single submission's lifecycle through the grading pipeline. Sessions have the same status codes as submissions (see Student Guide, Section 5).

% ─────────────────────────────────────────────────────────────────────
\section{System Health}
% ─────────────────────────────────────────────────────────────────────

The platform exposes a health endpoint:

\begin{lstlisting}
GET /health
\end{lstlisting}

Response example:
\begin{lstlisting}
{
  "status": "ok",
  "database": "ok",
  "redis": "ok",
  "version": "2.0.0"
}
\end{lstlisting}

\begin{itemize}
  \item \texttt{status: "ok"} -- All systems operational
  \item \texttt{status: "degraded"} -- One or more services down; check database/Redis
  \item Navigate to \textbf{Health} in the admin sidebar for a UI view of this data.
\end{itemize}

% ─────────────────────────────────────────────────────────────────────
\section{Security Operations}
% ─────────────────────────────────────────────────────────────────────

\subsection{Rotating JWT Secret}

\begin{enumerate}
  \item Generate a new secret: \texttt{python -c "import secrets; print(secrets.token\_hex(64))"}
  \item Update \texttt{JWT\_SECRET\_KEY} in the Railway environment and EC2 \texttt{.env}.
  \item Restart the API service. \textbf{All existing sessions will be invalidated} -- users must log in again.
\end{enumerate}

\begin{dangerbox}
  Rotating the JWT secret logs out every user simultaneously. Schedule this during off-hours and notify users in advance.
\end{dangerbox}

\subsection{Rotating the Proof Signing Key}

The \texttt{PROOF\_SIGNING\_KEY} is embedded in compiled grader binaries. Rotating it requires rebuilding and redistributing all grader binaries. Coordinate with the grading team before rotating this key.

\subsection{Resetting a Student Password}

Currently, password resets must be done via direct database update or by re-importing the student via CSV (which resets the password to their email). A self-service reset flow is not yet implemented.

\begin{lstlisting}[language=bash]
# Connect to PostgreSQL and update a password hash
docker exec -it grading_postgres psql -U grading_user -d grading_db

-- In psql:
UPDATE student SET hashed_password = '<bcrypt_hash>' 
WHERE roll_number = '2025CS001';
\end{lstlisting}

% ─────────────────────────────────────────────────────────────────────
\section{Quick Reference}
% ─────────────────────────────────────────────────────────────────────

\begin{tcolorbox}[colback=adminRed!5, colframe=adminRed, title={\faBookmark\enspace Admin Quick Reference}]
\begin{tabular}{ll}
\textbf{Default admin login:}   & \texttt{eyantrastaff@gmail.com} \\
\textbf{Default admin pass:}    & \texttt{eyantrastaff@gmail.com} (change immediately!) \\
\textbf{Health endpoint:}        & \texttt{GET /health} \\
\textbf{Admin submissions:}      & \texttt{GET /api/v1/admin/submissions} \\
\textbf{Create mentor:}          & \texttt{POST /api/v1/admin/mentors} \\
\textbf{Admin assignment edit:}  & \texttt{PATCH /api/v1/assignments/admin/\{id\}} \\
\textbf{Archive assignment:}     & \texttt{DELETE /api/v1/assignments/admin/\{id\}} \\
\textbf{API Docs:}               & \texttt{/docs} (DEBUG mode only) \\
\end{tabular}
\end{tcolorbox}

% ─────────────────────────────────────────────────────────────────────
\end{document}
